OSF management

### 2021-02-02 osf/manage-osf.Rmd
:bento: - fix typos in datasets; add ratings data; upload to osf

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(osfr)
```

@@

## Knit Readmes

@@

```{r knit-all, message=FALSE, warning=FALSE}
files <- list.files("./osf/data", pattern = "[.]Rmd$", recursive = T, full.names = T)

@@

## Upload Readmes to the OFS repo

```{r readmes}
# A loop would be better

@@

for (tlist in tlists) {
  speaker <- str_sub(tlist, 20, 21)
  tbl <- read_csv(tlist) %>%
    mutate(
      speaker = speaker,
      trial = row_number()
    ) %>%
    left_join(y = typ) %>%
    select(speaker, trial, condition, typicality, everything())

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(osfr)
library(speakr)
```

@@

@@

```{r knit-readmes, message=FALSE, warning=FALSE}
files <- list.files("./osf/data", pattern = "[.]Rmd$", recursive = T, full.names = T)

@@

```{r upload-readmes}
# A loop would be better

@@

for (tlist in tlists) {
  speaker <- str_sub(tlist, 20, 21)
  tbl <- read_csv(tlist) %>%
    mutate(
      speaker = speaker,
      trial = row_number()
    ) %>%
    left_join(y = typ) %>%
    select(speaker, trial, condition, typicality, everything()) %>%
    left_join(y = ratings_summary, by = c("target_name" = "object", "target_colour" = "colour"))
